### 2017-03-16 readme.Rmd
update to readme

p_bias_cell <- p_bias*area(tassie_preds)*1000
jet.colors <- colorRampPalette(rev(RColorBrewer::brewer.pal(11 , "Spectral")))
plot(p_bias_cell,col=jet.colors(100),main="s(z)")
```

>>>>

p_bias_cell <- p_bias*area(tassie_preds)*1000
jet.colors <- colorRampPalette(rev(RColorBrewer::brewer.pal(11 , "Spectral")))
plot(p_bias_cell,col=jet.colors(100),main="s(z)",
  xlim=c(144.5, 148.5), ylim=c(-43.8,-40.5))
```
